additional3D

### 2021-05-27 additional.Rmd
last reference additional asymmetric

 df <- read.csv("3Dlowdom.csv",sep = ",",skip = 6)
df2 <- read.csv("3Dhighdom.csv",sep = ",",skip = 6)
leg <- read.csv("legend_sa_asym.csv",sep=";")[,1]
df_fin <- rbind(df,df2)
 names(df_fin)<- leg

# 
# df_t <- rbind(df_3D,df_fin)
# 
# 
# write.csv(df_t,"3D.csv",row.names = F)

@@

excl3D <- names(df_fin) %in% c("run", "density","step")
df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

vars <- c("de_sq_bl","dv_sq_bl","et_sq_bl","vl_sq_bl")
df_sqbl <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5)
df_high <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20)

lowE <- plot_ly(df_sqbl)  %>%
  add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$de_sq_bl,
            scene = "scene1",
                                        name = "Ethnic",
                                       type="scatter3d",
                                       mode="markers",
                                     marker = list(cmin=0,cmax=1,
                                                   # colorscale = "Reds",
                                     colorscale =  list(
                                        c(0,'pink'),
                                        c(0.25,'red'),
                                        c(0.5,'green'),
                                        c(0.75,'blue'),
                                        c(1, 'purple')),
                                       color= df_sqbl$et_sq_bl, showscale = T)

            )  %>% 
  layout(showlegend = F,
         title="Ethnic",
         scene = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Cluster")))

 lowV<- plot_ly(df_sqbl)  %>%   add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$dv_sq_bl,
                                          scene =  "scene2",
                                     name = "Value",
                                     type="scatter3d",
                                     mode="markers",
                                    marker = list(cmin=0,cmax=1,
                                                   # colorscale = "Reds",
                                     colorscale =  list(
                                        c(0,'pink'),
                                        c(0.25,'red'),
                                        c(0.5,'green'),
                                        c(0.75,'blue'),
                                        c(1, 'purple')),
                                       color= df_sqbl$et_sq_bl, showscale = T)

            )  %>% 
       layout(showlegend = T,
         title="",
         scene = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Cluster")))

A <- subplot(lowE,lowV) %>% layout(annotations = list(
 list(x = 0.2 , y = 1 , text = "Ethnic", showarrow = F, xref='paper', yref='paper'),
  list(x = 0.8 , y = 1, text = "Value", showarrow = F, xref='paper', yref='paper'))
)

   ###

high <- plot_ly(df_high)  %>% add_trace(x=df_high$fraction_blue,y=df_high$circle_orange,z=df_high$de_sq_bl,color= df_high$et_sq_bl,
                                       type="scatter3d",
                                       mode="markers",
                                       marker = list( colorscale = 'Reds', showscale = T))  %>%
  add_trace(x=df_high$fraction_blue,y=df_high$circle_orange,z=df_high$dv_sq_bl,color= df_high$vl_sq_bl,
              type="scatter3d",
                                       mode="markers",
                                      marker = list( colorscale = 'Greens', showscale = TRUE))  %>%
  layout(legend = list(orientation = 'h'),
         title="high",
         scene = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Cluster")))

low
high

```{r 3Dsimple, fig.cap="3D pictures", echo = FALSE}

excl3D <- names(df_fin) %in% c("run", "density","step")
df_fin <- df_fin[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

vars <- c("de_sq_or","dv_sq_or","et_sq_or","vl_sq_or")
df_sqbl <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5)
df_high <- cbind(df_fin[,1:11],df_fin[,vars]) %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20)

low <- plot3D::scatter3D(x = df_sqbl$fraction_blue, y = df_sqbl$circle_orange, z = df_sqbl$de_sq_or, colvar = df_sqbl$et_sq_or, col = ramp.col (col = c("grey", "blue"), n = 100, alpha = 1), pch=20, cex= 2, phi = 0)

>>>>

@@

df_3D_low <- df_3D %>% filter(val_lib_loc==5,val_lib_min==5,eth_con_loc == 5,eth_con_min == 5,eth_lib_loc ==0,eth_lib_min==0) 
df_3D_high <- df_3D %>% filter(val_lib_loc==20,val_lib_min==20,eth_con_loc == 20,eth_con_min == 20,eth_lib_loc ==0,eth_lib_min==0)

xx <- ~fraction_blue
yy <- ~circle_orange
zz <- ~de_sq_or
cols <- ~et_sq_or
zzv <- ~dv_sq_or
colsv <- ~vl_sq_or
tt <- "Conservative Minority"

D3 <- {
lowE <- plot_ly(df_3D_low)  %>%
  add_trace(x= xx,y= yy,z=zz,
            scene = "scene1",
            type="scatter3d",
             mode="markers",
             marker = list(
             colorscale = "Reds",
             color= cols, showscale =  T,
             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='bottom'))

            )  %>%
  layout(showlegend = F,
         #title="Ethnic",
         "scene1" = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
      zaxis = list(title = "Ethnic Cluster")))

 lowV<- plot_ly(df_3D_low)  %>%   add_trace(x=xx,y=yy,z=zzv,
             scene =  "scene2",
             type="scatter3d",
             mode="markers", 
             marker = list( 
             colorscale = "Blues",
             color= colsv , showscale = T, reversescale=T,
             colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='bottom'))
            )  %>% 
       layout(showlegend = F,
         "scene2" = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority"  ,autorange = "reversed"),
      zaxis = list(title = "Value Cluster")))

highE <- plot_ly(df_3D_high)  %>%
  add_trace(x=xx,y=yy,z=zz,
            scene = "scene3",
            type="scatter3d",
             mode="markers",
             marker = list(
             colorscale = "Reds",
             color= cols, showscale =  T,
             colorbar=list(title = "Ethnic \nExposure" ,x = -0.1,  len = 0.5, yanchor='top'))

            )  %>%
  layout(showlegend = F,
         #title="Ethnic",
         "scene3" = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority" ,autorange = "reversed"),
      zaxis = list(title = "Ethnic Cluster")))

 highV<- plot_ly(df_3D_high)  %>%   
    add_trace(x=xx,y=yy,z=zz,
     scene =  "scene4",
     type="scatter3d",
     mode="markers", 
     marker = list( 
     colorscale = "Blues",
     color= colsv , showscale = T, reversescale=T,
      colorbar=list(title = "Value  \nExposure", len=0.5, yanchor='top'))
            )  %>% 
       layout(showlegend = F,
         "scene4" = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority"   ,autorange = "reversed"),
      zaxis = list(title = "Value Cluster")))

subplot(lowE, lowV,  highE, highV) %>%

   layout(scene = list(domain=list(x=c(0,0.5),y=c(0.5,1)),zaxis = list(title = "Ethnic Cluster")),
         scene2 = list(domain=list(x=c(0.5,1),y=c(0.5,1))),
         scene3 = list(domain=list(x=c(0,0.5),y=c(0,0.5))),
         scene4 = list(domain=list(x=c(0.5,1),y=c(0,0.5)))
         ) %>%

  layout(annotations = list(
  text = tt,
  font = list(size = 18),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

) %>%
  layout(annotations = list(
  text = "High Randomness",
  font = list(size = 15),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 0.5,
  showarrow = FALSE
))%>%
  layout(annotations = list(
  text = "Low Randomness",
  font = list(size = 15),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 0,
  showarrow = FALSE
)

)
}
